\RequirePackage{pdfmanagement-testphase}
\DeclareDocumentMetadata{uncompress,pdfversion=2.0}

%:
%:
\documentclass[11pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{tagpdf}
\tagpdfsetup{activate,paratagging,interwordspace}
\usepackage{fancyhdr}
\usepackage{hyperref}
\newcommand{\compactlist}{\setlength{\itemsep}{0pt} \setlength{\parskip}{0pt} \setlength{\leftskip}{-1em}}

\usepackage[top=0.8in, bottom=0.8in,  left=1in, right=1in]{geometry}
\usepackage{pdfpages}
\lhead{MATH 2753 -- Tech Prof Math Stat}
\rhead{Fall 2023}
\chead[RE]{\quad\textbf{Project: Debate}}
\cfoot{}

\pagestyle{fancy}
\begin{document}
\paragraph{Overview.} We will work on the following project outside of class over the next few weeks. This assignment is due and your presentation will be given on \textbf{\underline{{Monday,~Oct.~23}}}.  \textbf{Detailed submission instructions will follow - watch email and D2L.}

\paragraph{Which is better?} You and a partner will address one of these difficult mathematical questions.  This is not an exhaustive list, and no two debates should be repeated.  Please see me to verify your choice of topic.

\begin{itemize} \compactlist
\item Which is better \(1\) or \(0\)?
\item Which is better \(e\) or \(\pi\) (or \(\tau\))?
\item Which is better \(\displaystyle\int f(x)\,dx\) or \(\dfrac{df}{dx}\)?
\item Which is better \(\displaystyle\int f(x)\,dx\) or \(\displaystyle \int_a^b f(x)\, dx\)?
\item Who is better Newton or Leibniz?
\item Which is better pure mathematics or applied mathematics?
\item Which is better algebra or linear algebra?
\item Which is better multiplication or division?
\item Which is better the product rule or the chain rule?
\item Which is better integration by parts or tabular integration?
\item Which is better the Fundamental Theorem of Calculus or of Algebra?
\item Which are better negative  or positive numbers?
\item Which are better irrational or rational numbers?
\item Which are better powers of 2 or powers of 10?
\item Which are better decimals or fractions?
\item Careers in math (e.g., actuary vs professor)?
\item Almost any other relevant dichotomy (pairs) or trichotomy (triples).
\end{itemize}
%
\paragraph{Instructions.}  You and a partner(s) will craft a beamer presentation to be given in 5 to 6 minutes total, to the class\footnote{If necessary you may submit a pre-recorded video, likely recorded at private, virtual meetings with me and your partner(s) during class, or sent separately from an out of class recording.  You will have the opportunity (this is required, actually) to watch and critique other presentations posted to D2L.} defending your positions on the debatable questions above.  Your presentation should contain images and at least simple mathematics (probably not detailed calculations or complicated notation).  Use a title page (with your real names), but no table of contents.  
\paragraph{Template.} Start with a blank document.  Get your information onto the screen \textit{then} focus on formatting.  Keep it simple, but interesting. I expect you to develop your own document.  You should be able to explain every single line of the code to me, if requested; this will not be possible unless you have written the document yourself.   
\end{document}