\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{fancyhdr} %% might need to comment this out
\usepackage{hyperref}
\usepackage{graphicx}

\usepackage[top=1in, bottom=0.8in, left=1in, right=1in]{geometry}
\newcommand{\compactlist}{\setlength{\itemsep}{0pt} \setlength{\parskip}{0pt} \setlength{\leftskip}{-1em}}

%% might need to commend out next 4 lines if you don't have fancyhdr package
\lhead{MATH 2753 -- Tech Prof Math Stat}
\rhead{Fall 2023}
\chead[RE]{{\bf Debate Rubric}}
\cfoot{}

\pagestyle{fancy}%% might need to comment this out
\begin{document}
\noindent\textbf{Insert your name here}

\paragraph{Important!} I will be the only one to read these comments. I will summarize observations and share suggestions at the class level - nobody will read your exact words but me.  Write your answers below in sentence form, upload a pdf file to the D2L ``Debate Feedback'' folder (near where you uploaded your files and presentation videos.

\paragraph{Self-evaluation}
Give a brief description of yourself as a partner keeping in mind things like (you do not need to address all areas)
 \begin{itemize}\compactlist
 \item communication
 \item shared the workload/cooperation
 \item made original contributions 
 \item responded well to constructive criticism 
 \item completed tasks in a timely manner 
\end{itemize}

%% enter your response:

\vfill

\paragraph{Peer evaluation}
Address the performance of your partner(s) using items from the list of qualities above.

%% enter your response:

\vfill

\paragraph{Audience evaluation}
Consider the following elements of a presentation
\begin{itemize}\compactlist
\item appropriate tone, pace, and volume
\item presented relevant content
\item interaction between presenters
\item slides organized and easy to read
\item slides included appropriate content (math, images, tables)
\item all content was technically appropriate (no mathematical errors)
\end{itemize}
%
After watching the presentations, describe \textbf{one collective area for improvement} that could apply to one or more of the presentations. Describe \textbf{one collective strength} shared by some or all of the presentations.  Did you have a \textbf{favorite presentation}, if so, what was it and why was it your favorite?

%% enter your response below:

\vfill
\end{document}