\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fancyhdr}%% comment out if necessary
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[top=1in, bottom=0.8in,  left=1in, right=1in]{geometry}
\usepackage[]{anyfontsize}

\lhead{MATH 2753 -- Tech Prof Math Stat}%% comment out if necessary
\rhead{Fall 2023}%% comment out if necessary
\chead[RE]{{{\bf Hackathon }}}%% comment out if necessary
\cfoot{}%% comment out if necessary


\begin{document}
\pagestyle{fancy}%% comment out if necessary
\textbf{Your name:}\hspace{5cm}
\vspace{1cm}

\textbf{Instructions.}  Please assess a group member according to the categories below.  
\begin{itemize}
\item You will be graded for the overall activity based on the quality of the feedback you give and the grades and comments you earn.  Please be a productive group member and a fair evaluator.  
\item Your scores and comments are confidential.
\item Rate your assigned member on a zero to ten scale, with ten being a high score indicating outstanding effort for the indicated category.
\item Perform this assessment in the last 5-10 minutes of the activity.
\end{itemize}
\begin{center}
\begin{tabular}{|p{1.2in}||p{1in}|| p{1in} | p{1in} | p{1in} |}
\cline{1-5}
 &  & \multicolumn{3}{c|}{Partner Names}\\
\cline{3-5}
& \centering Self &  &  & \\
\cline{1-5}
\bf Participation/\newline Activity & & & &  \\[12pt]
\cline{1-5}
\bf Cooperativity &  & & & \\[12pt]
\cline{1-5}
\bf Innovation &  & & & \\[12pt]
\cline{1-5}
\bf Intellectual \newline Contribution  & & & & \\[12pt]
\hline
\bf Other  & & & & \\[12pt]
\hline
\hline
\bf Overall & & &  &  \\[12pt]
\cline{1-5}
\end{tabular}
\end{center}

\paragraph{Other comments.} Please give specific comments about your own participation/performance and that of each group member.  If everyone gets all 10's, that's fine, just be sure to tell me why.


\newpage
\begin{center}
\begin{tabular}{|p{1.2in}| p{1in} | p{1in} | p{1in} |}
\cline{1-4}
  & \multicolumn{3}{c|}{Additional Partner Names}\\
\cline{2-4}
& \centering  &  & \\
\cline{1-4}
\bf Participation/\newline Activity & & &  \\[12pt]
\cline{1-4}
\bf Cooperativity &  & & \\[12pt]
\cline{1-4}
\bf Innovation &  & & \\[12pt]
\cline{1-4}
\bf Intellectual \newline Contribution  & & & \\[12pt]
\hline
\bf Other  & & & \\[12pt]
\hline
\hline
\bf Overall & &  &  \\[12pt]
\cline{1-4}
\end{tabular}
\end{center}
\paragraph{Other comments.} Please give specific comments about your own participation/performance and that of each group member.  If everyone gets all 10's, that's fine, just be sure to tell me why.


\end{document}